Characterizing Stellar Streams by ML

### 2023-08-31 src/tex/ms.tex
[showyourwork] overleaf sync

        The custom model framework combines for each model a neural network with
        Bayesian probability functions. The latter are set by the model type,
        e.g. the Gaussian model has a Gaussian likelihood function, but the
        former, the neural network, is set and determined by the user. So long
        as the network has the correct number of inputs (e.g. one for $\phi_1$)
        and outputs (one per parameter), any feed-forward network may be used.
        Our default choice, and for which we provide a helper function, is an
        MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh})
        blocks. This is illustrated in \autoref{table:mlp_structure}.
        % FIXME! reference not being picked up correctly.
        Dropout layers are used to prevent network co-adaptation and
        over-fitting. Dropout works by randomly zeroing out nodes in the
        network, decreasing the importance of any single node, encouraging
        instead emergent patterns across the network.  One model for which the
        lin-tanh-dropout network cannot be used is the normalizing flow used in
        the photometric background model
        (\autoref{sub:method:photometric_model:off_stream}). Here we use the
        \package{nflows} package, with a conditional diagonal normal base
        distribution and composite transform network of a reverse permutation
        and masked affine auto-regressive transform layers. As noted in our data
        availability statement, all the codes used in this paper are bundled by
        \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
        in a public repository at \GitHubURL{}. We will describe for each
        stream model specifics relevant to that stream but refer readers to the
        publicly-available code itself for code implementation details.
        % TODO: Maybe more details in the Appendix?

@@

    \subsection{Model Specification} \label{sub:resultes_mock:model}

@@

>>>>

        The custom model framework combines for each model a neural network with
        Bayesian probability functions. The latter are set by the model type,
        e.g. the Gaussian model has a Gaussian likelihood function, but the
        former, the neural network, is set and determined by the user. So long
        as the network has the correct number of inputs (e.g. one for $\phi_1$)
        and outputs (one per parameter), any feed-forward network may be used.
        Our default choice, and for which we provide a helper function, is an
        MLP with a sequence of \texttt{Linear} \!\!\textrightarrow \texttt{Tanh}
        \!\!\textrightarrow \texttt{Dropout} (hereafter \texttt{LinTanh})
        blocks. This is illustrated in \autoref{table:mlp_structure}.
        % FIXME! reference not being picked up correctly.
        Dropout layers are used to prevent network co-adaptation and
        over-fitting. Dropout works by randomly zeroing out nodes in the
        network, decreasing the importance of any single node, encouraging
        instead emergent patterns across the network.  One model for which the
        lin-tanh-dropout network cannot be used is the normalizing flow used in
        the photometric background model
        (\autoref{sub:method:photometric_model:off_stream}). Here we use the
        \package{nflows} package, with a conditional diagonal normal base
        distribution and composite transform network of a reverse permutation
        and masked affine auto-regressive transform layers. As noted in our data
        availability statement, all the codes used in this paper are bundled by
        \href{https://github.com/showyourwork/showyourwork}{\package{showyourwork}}
        in a public repository at \url{\GitHubURL{}}. We will describe for each
        stream model specifics relevant to that stream but refer readers to the
        publicly-available code itself for code implementation details.
        % TODO: Maybe more details in the Appendix?

@@

    \subsection{Model Specification} \label{sub:results_mock:model}

@@

        \autoref{sec:results_mock:model}
